Wikipedia Text Mining and Entropy Analysis

### 2019-02-01 childes/childes_entropy.Rmd
dendrogram and slope plots

  if (role == "child") {
    lengths <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      mutate(length = str_count(stem, " ") + 1)

} else {
    lengths <- utterances %>%
      filter(speaker_role != "Target_Child") %>%
      mutate(length = str_count(stem, " ") + 1)
}

  tokens <- lengths %>% 
    filter(length >= min_length) %>%
    filter(length <= max_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, stem, token = stringr::str_split, pattern = " +") %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    filter(word_order <= length) %>% 
    summarise(n = n()) 
}

@@

  if (role == "child") {
    lengths <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      mutate(length = str_count(gloss, " ") + 1)

} else {
    lengths <- utterances %>%
      filter(speaker_role != "Target_Child") %>%
      mutate(length = str_count(gloss, " ") + 1)
}

  tokens <- lengths %>% 
    filter(length >= min_length) %>%
    filter(length <= max_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, stem, token = stringr::str_split, pattern = " +") %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    filter(word_order <= length) %>% 
    summarise(n = n()) 
}

>>>>

  if (role == "child") {
    sub_utterances <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      mutate(length = str_count(stem, pattern = " +") + 1)

} else {
    sub_utterances <- utterances %>%
      filter(speaker_role != "Target_Child") %>%
      mutate(length = str_count(stem, pattern = " +") + 1)
}

  tokens <- sub_utterances %>%
    filter(length == target_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, stem) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(word_order, word) %>%
    filter(word_order <= length)

  tokens %>%
    summarise(n = n()) %>%
    tidyboot(summary_function = function(x) x %>% 
               summarise(entropy = entropy(n, unit = "log2")),
             statistics_functions = function(x) x %>%
             summarise_at(vars(entropy), funs(ci_upper, ci_lower))) %>%
    mutate(role = role, length = target_length)
}

@@

  if (role == "child") {
    sub_utterances <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      mutate(length = str_count(gloss, pattern = " +") + 1)

} else {
    sub_utterances <- utterances %>%
      filter(speaker_role != "Target_Child") %>%
      mutate(length = str_count(gloss, pattern = " +") + 1)
}

  tokens <- sub_utterances %>%
    filter(length == target_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, gloss) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(word_order, word) %>%
    filter(word_order <= length)

  tokens %>%
    summarise(n = n()) %>%
    tidyboot(summary_function = function(x) x %>% 
               summarise(entropy = entropy(n, unit = "log2")),
             statistics_functions = function(x) x %>%
             summarise_at(vars(entropy), funs(ci_upper, ci_lower))) %>%
    mutate(role = role, length = target_length)
}

### 2019-02-01 wiki_entropy/wiki_clustering.Rmd
dendrogram and slope plots

```{r imputation for glm}
imputed_result <- wf_df %>%
  select(language, feature, value) %>%
  ungroup() %>% 
  spread(feature, value) %>% 
  column_to_rownames("language") %>%
  sapply(as.factor) %>%
  as_data_frame() %>%
  MIMCA(ncp = 7, maxiter = 999)

>>>>

```{r imputation for glm}
dendro_langs <- wf_sub_langs$language

wk_clust_tree <- wkpd %>% 
              filter(Language %in% dendro_langs) %>%
              column_to_rownames(var = "Language") %>%
              dist() %>%
              hclust("ward.D2")

wk_clust_tree %>% plot(hang = -1)

imputed_result <- wf_df %>%
  select(language, feature, value) %>%
  ungroup() %>% 
  spread(feature, value) %>% 
  column_to_rownames("language") %>%
  sapply(as.factor) %>%
  as_data_frame() %>%
  MIMCA(ncp = 7, maxiter = 999)
